---
title: "Movie Reviews"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


First installed all needed packages.

```{r}
library(dplyr)
# install.packages("tidyverse")
library(tidyverse)

```

Then we read the movie genres data into R and viewed the data to see what question could be answered.

```{r}

my_data <- read.csv("data/movie_genres.csv")

head(my_data)
```

The question we answered were "What genres include three or more movies?"
We created a new data frame that showed the movie count of 3 or more for those particular genres.

```{r}
top_movies <- my_data %>%
  group_by(genre) %>%
  summarise(movie_count = n()) %>%
  filter(movie_count >= 3)
```

Here we rearranged the data to show the genres in order by count instead of alphabetical order. 

```{r}

top_movies <- top_movies %>%
  arrange(desc(movie_count))

top_movies$genre <- reorder(top_movies$genre, top_movies$movie_count)

```

Here we plotted the results in a histogram and included the order as assigning labels and giving each bar a specific color. 

```{r}
# install.packages("ggplot2")
library(ggplot2)

ggplot(top_movies, aes(x = genre, y = movie_count, fill = genre)) + 
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Genres with 3 or More Movies", 
       x = "genre",
       y = "count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)
  )
```



